14th International Satisfiability Modulo Theories Competition (SMT-COMP 2019): Rules and Procedures

### 2019-04-11 rules/rules19.tex
add todos

The rest of this document, revised from the previous
version,\footnote{Earlier versions of this document include
  contributions from Clark Barrett, Roberto Bruttomesso, David Cok,
  Sylvain Conchon, David D{\'e}harbe, Morgan Deters, Alberto Griggio,
  Matthias Heizmann, Aina Niemetz, Albert Oliveras, Giles Reger, Aaron Stump,
	and Tjark Weber.}  describes the rules and competition procedures for
SMT-COMP~2019.
The principal changes from the previous competition rules are the following:
\begin{itemize}
  \item {\it Renaming of Tracks.} This year, the track previously known as
    `Main Track` will be renamed to \emph{\main Track}, and the previous
    `Application Track' will be renamed to \emph{\incremental Track}.
    \emph{Rationale:} We believe the current names are misleading, as the
    previous `Main Track' also contains problems coming from applications.
    Additionally, having it called `Main' de-emphasizes the importance of the
    other tracks and use cases of SMT.

@@

\header{System description.}
%
As part of the submission, SMT-COMP entrants are \emph{required} to provide a
short (1–-2 pages) description of the system.  This should include a list of
all authors of the system, their present institutional affiliations, and any
appropriate acknowledgements.  The programming language(s) and basic SMT
solving approach employed should be described (e.g., lazy integration of a
Nelson-Oppen combination with SAT, translation to SAT, etc.).  System
descriptions should also include a URL for a web site for the submitted tool.
System descriptions must be submitted until the final solver deadline System
descriptions will be made publicly available.

@@

\todo{Add information that these solver versions will be made available
on the smt-comp website for archiving purposes? What are the implications of
this?}

@@

@@

The benchmark script is in the concrete syntax of the SMT-LIB format,
version~2.6, though with a restricted set of commands.  A benchmark
script is a text file containing a sequence of SMT-LIB commands that
satisfies the following requirements:
%
\begin{enumerate}
\item
  \begin{enumerate}
  \item In the \main and \ucore tracks, there may be a single
    \akey{(set-option :print-success ...)} command.  Note that
    \texttt{success} outputs are ignored by the post-processor used by
    the competition.\footnote{SMT-LIB~2.6 requires solvers to produce
      a \texttt{success} answer after each \akey{set-logic},
      \akey{declare-sort}, \akey{declare-fun} and \akey{assert}
      command (among others), unless the option \akey{:print-success}
      is set to false.  Ignoring the \texttt{success} outputs allows
      for submitting fully SMT-LIB~2.6 compliant solvers without the
      need for a wrapper script, while still allowing entrants of
      previous competitions to run without changes.}
  \item In the incremental track, the \akey{:print-success} option
    must not be disabled.  The trace executor will send an initial
      \akey{(set-option :print-success true)} command to the solver.
  \end{enumerate}
\item In the \ucore Track, there is a single \akey{(set-option
  :produce-unsat-cores true)} command.
\item The (single) \akey{set-logic} command setting the benchmark's
  logic is the first command after any \akey{set-option} commands.
\item The script may contain any number of \akey{set-info} commands.
\item The script may contain any number of \akey{declare-sort} and
  \akey{define-sort} commands.  All sorts declared or defined with
  these commands must have zero arity.
\item The script may contain any number of \akey{declare-fun} and
  \akey{define-fun} commands.
\item If the benchmark's logic features algebraic datatypes, the
  script may contain any number of \akey{declare-datatype(s)}
  commands.
\item The script may contain any number of \akey{assert} commands.
  All formulas in the script belong to the benchmark's logic, with any
  free symbols declared in the script.
\item
  \begin{enumerate}
    \item In all tracks except the \ucore Track,  named terms (i.e., terms
      with the \akey{:named} attribute) are not used.
    \item In the \ucore Track, top-level assertions may be named.
  \end{enumerate}
\item
  \begin{enumerate}
  \item In all tracks except the \incremental Track, there is exactly one
    \akey{check-sat} command. \todo{is that true for the challenge track?}
  \item In the incremental track, there are one or more
    \akey{check-sat} commands.  There may also be zero or more
    \akey{push 1} commands, and zero or more \akey{pop 1} commands,
    consistent with the use of those commands in the SMT-LIB standard.
  \end{enumerate}
\item In the \ucore Track, the \akey{check-sat} command (which is
  always issued in an unsatisfiable context) is followed by a single
  \akey{get-unsat-core} command.
\item In the \mval Track, the \akey{check-sat} command (which is
  always issued in a satisfiable context) is followed by a single
  \akey{get-model} command. \todo{Liana: please verify}
\item The script may optionally contain an \akey{exit} command as its
  last command.  In the incremental track, this command must not be
  omitted.
\item No other commands besides the ones just mentioned may be used.
\end{enumerate}
%
The SMT-LIB format specification is available from the ``Standard''
section of the SMT-LIB website~\cite{SMT-LIB}.  Solvers will be given
formulas only from the divisions into which they have been entered.

\header{Time and memory limits.}
%
Each SMT-COMP solver will be executed on a dedicated processor of a
competition machine, for each given benchmark, up to a fixed
wall-clock time limit~$T$.  Each processor has 4 cores.  Detailed
machine specifications are available on the competition web site.

The time limit~$T$ will be 40~minutes of wall-clock time per solver/benchmark
pair in the \main, \incremental and \ucore tracks, \todo{XX}~minutes in the
\challenge Track, and \todo{XX}~minutes in the \mval Track
\todo{Need to elaborate how time is split? Do we
need two time limits here, one for solving and one for
validation?}.\footnote{The time limit may be
adjusted once we know the number of competition entrants and eligible
benchmarks.}  Solvers that take more than this time limit will be killed.
Solvers are allowed to spawn other processes; these will be killed at
approximately the same time as the first started process.

@@

In order to facilitate the evaluation of solvers in this track, we will set up
a ``simulation'' of the aforementioned interaction.  Each benchmark represents
a realistic communication trace, containing multiple \akey{check-sat} commands
(possibly with corresponding \akey{push 1} and \akey{pop 1} commands). It is
parsed by a (publicly available) \emph{trace executor}\footnote{\todo{link}},
which serves the following purposes: \begin{itemize} \item it simulates the
online interaction by sending single queries to the SMT solver (through stdin);
\item it prevents ``look-ahead'' behaviors of SMT solvers;
\item it records time and answers for each command;
\item it guarantees a fair execution for all solvers by abstracting
  from any possible crash, misbehavior, etc.\ that might happen in the
  verification framework.
\end{itemize}

@@

\todo{time limit}
The \challenge Track will follow the same rules as the \main Track,
with two exceptions: benchmark selection and the time limit. The track will run on
all SMT-LIB benchmarks that have an unknown status and that have been tagged as being
 \emph{industrial}. Additionally we will include benchmarks nominated by the community.
\lh{TODO: benchmark selection still needs discussion}
\lh{TODO: We didn't decide on what we do if only one solver gives an answer and we don't
know if the problem is sat/unsat}

@@

@@

\todo{We do not run non-competitive divisions.}

\header{Benchmark sources.}
%
Benchmarks for each division will be drawn from the SMT-LIB benchmark
library.  The \main Track will use a subset of all
\emph{non-incremental} benchmarks; the incremental track will use a
subset of all \emph{incremental} benchmarks.  The \ucore Track
will use unsatisfiable \main Track benchmarks, modified to use named
top-level assertions.
\todo{add information about how benchmarks are selected for the \mval,
\challenge, \ucore tracks, and the 24s, sat and unsat scores -- either here
or below}

@@

\header{Benchmark selection.}
%
The competition will use a large subset of SMT-LIB benchmarks.  The
benchmark pool is culled as follows:
\todo{add information about how benchmarks are selected for the \mval,
\challenge, \ucore tracks, and the 24s, sat and unsat scores}
\begin{enumerate}
\item \emph{Remove inappropriate benchmarks.} The competition
  organizers may remove benchmarks that are deemed inappropriate or
  uninteresting for competition, or cut the size of certain benchmark
  families to avoid their over-representation.  SMT-COMP attempts to
  give preference to benchmarks that are ``real-world,'' in the sense
  of coming from or having some intended application outside SMT.
\item \todo{\emph{Remove benchmarks solved by all solvers within 1s in the previous year}}
\end{enumerate}
%
\todo{update with the new benchmark selection rules}
All remaining benchmarks are used for the competition.  There will be
no further selection of benchmarks, e.g., based on benchmark
difficulty or benchmark category.

@@

>>>>

The rest of this document, revised from the previous
version,\footnote{Earlier versions of this document include
  contributions from Clark Barrett, Roberto Bruttomesso, David Cok,
  Sylvain Conchon, David D{\'e}harbe, Morgan Deters, Alberto Griggio,
  Matthias Heizmann, Aina Niemetz, Albert Oliveras, Giles Reger, Aaron Stump,
	and Tjark Weber.}  describes the rules and competition procedures for
SMT-COMP~2019.
The principal changes from the previous competition rules are the following: \todo{Aina in charge of this section}
\begin{itemize}
  \item {\it Renaming of Tracks.} This year, the track previously known as
    `Main Track` will be renamed to \emph{\main Track}, and the previous
    `Application Track' will be renamed to \emph{\incremental Track}.
    \emph{Rationale:} We believe the current names are misleading, as the
    previous `Main Track' also contains problems coming from applications.
    Additionally, having it called `Main' de-emphasizes the importance of the
    other tracks and use cases of SMT.

@@

\header{System description.}
%
As part of the submission, SMT-COMP entrants are \emph{required} to provide a
short (1–-2 pages) description of the system.  This should include a list of
all authors of the system, their present institutional affiliations, and any
appropriate acknowledgements.  The programming language(s) and basic SMT
solving approach employed should be described (e.g., lazy integration of a
Nelson-Oppen combination with SAT, translation to SAT, etc.).  System
descriptions should also include a URL for a web site for the submitted tool.
System descriptions must be submitted until the final solver deadline System
descriptions will be made publicly available. \todo{Giles: Include licence information - minimum requirement: licence must allow to run the binary for evaluation purposes}

@@

@@

\header{Competition Website}

\todo{Giles: Add text about the fact that we will use the competition website to include links to tools, announce results etc... including archiving}
%

@@

The benchmark script is in the concrete syntax of the SMT-LIB format,
version~2.6, though with a restricted set of commands.  A benchmark
script is a text file containing a sequence of SMT-LIB commands that
satisfies the following requirements:
%
\begin{enumerate}
\item
  \begin{enumerate}
  \item In the \main and \ucore tracks, there may be a single
    \akey{(set-option :print-success ...)} command.  Note that
    \texttt{success} outputs are ignored by the post-processor used by
    the competition.\footnote{SMT-LIB~2.6 requires solvers to produce
      a \texttt{success} answer after each \akey{set-logic},
      \akey{declare-sort}, \akey{declare-fun} and \akey{assert}
      command (among others), unless the option \akey{:print-success}
      is set to false.  Ignoring the \texttt{success} outputs allows
      for submitting fully SMT-LIB~2.6 compliant solvers without the
      need for a wrapper script, while still allowing entrants of
      previous competitions to run without changes.}
  \item In the incremental track, the \akey{:print-success} option
    must not be disabled.  The trace executor will send an initial
      \akey{(set-option :print-success true)} command to the solver.
  \end{enumerate}
\item In the \ucore Track, there is a single \akey{(set-option
  :produce-unsat-cores true)} command.
\item The (single) \akey{set-logic} command setting the benchmark's
  logic is the first command after any \akey{set-option} commands.
\item The script may contain any number of \akey{set-info} commands.
\item The script may contain any number of \akey{declare-sort} and
  \akey{define-sort} commands.  All sorts declared or defined with
  these commands must have zero arity.
\item The script may contain any number of \akey{declare-fun} and
  \akey{define-fun} commands.
\item If the benchmark's logic features algebraic datatypes, the
  script may contain any number of \akey{declare-datatype(s)}
  commands.
\item The script may contain any number of \akey{assert} commands.
  All formulas in the script belong to the benchmark's logic, with any
  free symbols declared in the script.
\item
  \begin{enumerate}
    \item In all tracks except the \ucore Track,  named terms (i.e., terms
      with the \akey{:named} attribute) are not used.
    \item In the \ucore Track, top-level assertions may be named.
  \end{enumerate}
\item
  \begin{enumerate}
  \item In all tracks except the \incremental Track, there is exactly one
    \akey{check-sat} command.
  \item In the incremental track, there are one or more
    \akey{check-sat} commands.  There may also be zero or more
    \akey{push 1} commands, and zero or more \akey{pop 1} commands,
    consistent with the use of those commands in the SMT-LIB standard.
  \end{enumerate}
\item In the \ucore Track, the \akey{check-sat} command (which is
  always issued in an unsatisfiable context) is followed by a single
  \akey{get-unsat-core} command.
\item In the \mval Track, the \akey{check-sat} command (which is
  always issued in a satisfiable context) is followed by a single
  \akey{get-model} command.
\item The script may optionally contain an \akey{exit} command as its
  last command.  In the incremental track, this command must not be
  omitted.
\item No other commands besides the ones just mentioned may be used.
\end{enumerate}
%
The SMT-LIB format specification is available from the ``Standard''
section of the SMT-LIB website~\cite{SMT-LIB}.  Solvers will be given
formulas only from the divisions into which they have been entered.

\header{Time and memory limits.} \todo{Aina: Move all time and memory limits to the individual sections and forward reference from here}
%
Each SMT-COMP solver will be executed on a dedicated processor of a
competition machine, for each given benchmark, up to a fixed
wall-clock time limit~$T$.  Each processor has 4 cores.  Detailed
machine specifications are available on the competition web site.

The time limit~$T$ will be 40~minutes of wall-clock time per solver/benchmark
pair in the \main, \incremental and \ucore tracks, \todo{12 hours} in the
\challenge Track, and \todo{40 + 5 as in Unsat core}~minutes in the \mval Track \footnote{The time limit may be
adjusted once we know the number of competition entrants and eligible
benchmarks.}  Solvers that take more than this time limit will be killed.
Solvers are allowed to spawn other processes; these will be killed at
approximately the same time as the first started process.

@@

In order to facilitate the evaluation of solvers in this track, we will set up
a ``simulation'' of the aforementioned interaction.  Each benchmark represents
a realistic communication trace, containing multiple \akey{check-sat} commands
(possibly with corresponding \akey{push 1} and \akey{pop 1} commands). It is
parsed by a (publicly available) \emph{trace executor},
which serves the following purposes: \begin{itemize} \item it simulates the
online interaction by sending single queries to the SMT solver (through stdin);
\item it prevents ``look-ahead'' behaviors of SMT solvers;
\item it records time and answers for each command;
\item it guarantees a fair execution for all solvers by abstracting
  from any possible crash, misbehavior, etc.\ that might happen in the
  verification framework.
\end{itemize}

@@

\todo{time limit}
The \challenge Track will follow the same rules as the \main Track,
with two exceptions: benchmark selection and the time limit. The track will run on benchmarks nominated by the community.
\lh{TODO: benchmark selection still needs discussion}
\lh{TODO: scored in the same way as main track (mention later not here)}

@@

\todo{Liana - check if we can use the SMT-LIB standard and if so say that we will here, or if we need slight changes state them here.}

@@

\todo{Aina: We do not run non-competitive divisions.}

\header{Benchmark sources.}
%
Benchmarks for each division will be drawn from the SMT-LIB benchmark
library.  The \main Track will use a subset of all
\emph{non-incremental} benchmarks; the incremental track will use a
subset of all \emph{incremental} benchmarks.  The \ucore Track
will use unsatisfiable \main Track benchmarks, modified to use named
top-level assertions.

@@

\header{Benchmark selection.} \todo{Antti covers this section}
%
The competition will use a large subset of SMT-LIB benchmarks.  The
benchmark pool is culled as follows:
\todo{add information about how benchmarks are selected for the \mval,
\challenge, \ucore tracks, and the 24s, sat and unsat scores}
\begin{enumerate}
\item \emph{Remove inappropriate benchmarks.} The competition
  organizers may remove benchmarks that are deemed inappropriate or
  uninteresting for competition, or cut the size of certain benchmark
  families to avoid their over-representation.  SMT-COMP attempts to
  give preference to benchmarks that are ``real-world,'' in the sense
  of coming from or having some intended application outside SMT.
\item \todo{\emph{Remove benchmarks solved by all solvers within 1s in the previous year}}
\end{enumerate}
%
\todo{update with the new benchmark selection rules}
All remaining benchmarks are used for the competition.  There will be
no further selection of benchmarks, e.g., based on benchmark
difficulty or benchmark category.

@@

\todo{add information about how benchmarks are selected for the \mval,
\challenge, \ucore tracks, and the 24s, sat and unsat scores -- either here
or below}

\todo{For Unsatcore remove all benchmarks with a single assertion, otherwise use same procedure as last year... check what that was}
